Kelompok 4_Praktikum_Pekan 8

### 2024-04-08 Project/Kelompok 4_Praktikum_Pekan 8.Rmd
Update

@@

## Poin 2 {.tabset}

@@

@@

  plots <- plot_distribution2(norm_samples[[which(sample_sizes == size)]], # Data Awal
                              norm_means[[which(sample_sizes == size)]], # Data Rataan
                              paste0("Distribusi Normal (n=", size, ")"), colors[1]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)

  plots <- plot_distribution2(unif_samples[[which(sample_sizes == size)]], # Data Awal
                             unif_means[[which(sample_sizes == size)]], # Data Rataan
                             paste0("Distribusi Seragam (n=", size, ")"), colors[2]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)

  plots <- plot_distribution2(exp_samples[[which(sample_sizes == size)]], # Data Awal
                             exp_means[[which(sample_sizes == size)]], # Data Rataan
                             paste0("Distribusi Eksponensial (n=", size, ")"), colors[3]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)

@@

>>>>

## Poin 1 & 2 {.tabset}

@@

## Poin 3 & 4 {.tabset}

@@

## Poin 5 {.tabset}

@@

  plots <- plot_distribution2(normal_data[[which(sample_sizes == size)]], # Data Rataan
                              paste0("Distribusi Normal (n=", size, ")"), colors[1]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)

  plots <- plot_distribution2(mixed_data1[[which(sample_sizes == size)]], # Data Rataan
                              paste0("Distribusi Campuran 1 (n=", size, ")"), colors[1]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)

  plots <- plot_distribution2(mixed_data2[[which(sample_sizes == size)]], # Data Rataan
                              paste0("Distribusi Campuran 2 (n=", size, ")"), colors[1]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)

  plots <- plot_distribution2(mixed_data3[[which(sample_sizes == size)]], # Data Rataan
                              paste0("Distribusi Campuran 3 (n=", size, ")"), colors[1]) # Title & Colors
  plots_for_size <- c(plots_for_size, plots)

@@

plot_grid(plotlist = all_plots, ncol = 8)
```
